Gaussian mean estimation in simulated data sets

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

Since the simulation experiments are computationally intensive, they
were implemented separately. (For instructions on re-running these
simulation experiments, see the README in the "dsc" directory of the
git repository). Here we create plots to summarize the results of
these experiments.

@@

```{r load-pkgs, message=FALSE, warning=FALSE}
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/signals.R")
```

@@

This plot reproduces Fig. 2 of the manuscript, which compares the
accuracy of the mean curves estimated from the data sets that were
simulated using the "Spikes" mean function with constant variance.

First, extract the results used to generate this plot.

```{r plot-1-extract-data}
homo.data.smash <-
  res[res$.id    == "sp.3.v1" &
      res$method == "smash.s8",]
homo.data.smash.homo <-
  res[res$.id    == "sp.3.v1" &
      res$method == "smash.homo.s8",]
homo.data.tithresh <-
  res[res$.id == "sp.3.v1" &
      res$method == "tithresh.homo.s8",]
homo.data.ebayes <-
  res[res$.id    == "sp.3.v1" &
      res$method == "ebayesthresh",]
homo.data.smash.true <-
  res[res$.id == "sp.3.v1" &
  res$method  == "smash.true.s8",]
homo.data <-
  res[res$.id == "sp.3.v1" &
  (res$method == "smash.s8" |
   res$method == "ebayesthresh" |
   res$method == "tithresh.homo.s8"),]
```

```{r plot-1-transform-data}
pdat <-
  rbind(data.frame(method      = "smash",
                   method.type = "est",
                   mise        = homo.data.smash$mise),
        data.frame(method      = "smash.homo",
                   method.type = "homo",
                   mise        = homo.data.smash.homo$mise),
        data.frame(method      = "tithresh",
                   method.type = "homo",
                   mise        = homo.data.tithresh$mise),
        data.frame(method      = "ebayesthresh",
                   method.type = "homo",
                   mise        = homo.data.ebayes$mise),
        data.frame(method      = "smash.true",
                   method.type = "true",
                   mise        = homo.data.smash.true$mise))
pdat <-
  transform(pdat,
            method = factor(method,
                            names(sort(tapply(pdat$mise,pdat$method,mean),
                                       decreasing = TRUE))))
```

@@

```{r plot-1-create, fig.height=4, fig.width=5}
p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
     geom_violin(fill = "skyblue",color = "skyblue") +
     geom_boxplot(width = 0.15,outlier.shape = NA) +
     scale_y_continuous(breaks = seq(6,16,2)) +
     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
                       guide = FALSE) +
     coord_flip() +
     labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
print(p)
```

@@

>>>>

Since the simulation experiments are computationally intensive, here
we only illustrate the application of the signal denoising methods,
and create plots summarizing the results of the full experiments; the
full experiments were implemented separately. (For instructions on
re-running these simulation experiments, see the README in the "dsc"
directory of the git repository).

@@

```{r load-pkgs, message=FALSE, warning=FALSE}
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/signals.R")
source("../code/gaussmeanest.functions.R")
```

@@

This plot reproduces Fig. 2 of the manuscript, which compares the
accuracy of the mean curves estimated from the data sets that were
simulated using the "Spikes" mean function with constant variance and
a signal-to-noise ratio of 3.

First, extract the results used to generate this plot, and transform
them into a data frame suitable for plotting using ggplot2.

```{r plot-1-extract-data}
pdat <- get.results.homosked(res,"sp.3.v1")
```

@@

```{r plot-1-create, fig.height=4, fig.width=5}
pdat <-
  transform(pdat,
            method = factor(method,
                            names(sort(tapply(pdat$mise,pdat$method,mean),
                                       decreasing = TRUE))))
p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
     geom_violin(fill = "skyblue",color = "skyblue") +
     geom_boxplot(width = 0.15,outlier.shape = NA) +
     scale_y_continuous(breaks = seq(6,16,2)) +
     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
                       guide = FALSE) +
     coord_flip() +
     labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
print(p)
```

@@

*TO DO: Add bar plots summarizing results from all 7 scenarios and 2
signal-to-noise ratios.*
